### 2021-04-09 paper/ase21/overview.tex
[ASE21] Till 3.1 without Figure 3 and subtype example

\paragraph{Syntax and Semantics} ECMAScript uses a variant of extended BNF
notations to describe JavaScript syntax.  $\jiset$ synthesizes AST structures
and JavaScript parsers from its lexical and syntactic productions.  Our tool
utilizes only AST structures to define AST types and to access corresponding
syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
abstract algorithms written in a structured natural language.  $\jiset$ compiles
them to functions of $\ires$, an untyped intermediate representation for
ECMAScript.  For brevity, we will formally define syntax and semantics of
a simplified $\ires$ in Section~\ref{sec:ires}.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase analysis precision using
refinement (Section~\ref{sec:analysis}) and how to detect type-related
specification bugs using four different checkers (Section~\ref{sec:checker}).
After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).

>>>>

\paragraph{Syntax and Semantics} ECMAScript uses a variant of extended BNF
notations to describe JavaScript syntax.  $\jiset$ synthesizes AST structures
and JavaScript parsers from its lexical and syntactic productions.  Our tool
utilizes only AST structures to define AST types and to access corresponding
syntax-directed algorithms.  For JavaScript semantics, ECMAScript contains
abstract algorithms written in a structured natural language.  $\jiset$ compiles
them to functions of $\ires$, an untyped intermediate representation for
ECMAScript.  For brevity, we will formally define syntax and semantics of
a modified $\ires$ in Section~\ref{sec:ires}.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase analysis precision using
refinement (Section~\ref{sec:analyzer}) and how to detect type-related
specification bugs using four different checkers (Section~\ref{sec:checker}).
After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).
